---
title: "Week09-SQLite-Exercise.ipynb"
output: html_document
---

```{r}
library(RSQLite)
library(tidyverse)
library(jsonlite)
library(DBI)
```
## Description

In this exersise, you will use the UK Parliment petition data stored in a SQLite database. The database contains the information on the number of signatuures for a number of most popular petitions as of 30 Nov, 2023.


## Download the dbfile

```{python}
#!wget "https://www.dropbox.com/scl/fi/3tv2vrnc1wxqm85gkubor/petition.sqlite?rlkey=drfhmgur1n3w7c891c3ujdeqp&dl=1" -O petition.sqlite
```

## Connect to the database

```{r}
conn <- dbConnect(SQLite(),dbname = "petition.sqlite")
```


## Check the database contents

Look up the `sqlite_master` table and figure out how many tables exist in this database. Also, get the understanding of the each table by browsing it.

```{r}
dbListTables(conn) # list tables

dbListFields(conn,"constituency") # find variable names of the table
dbListFields(conn,"signature") # find variable names of the table
dbListFields(conn,"petitionInfo") # find variable names of the table
```

```{sql connection=conn}
select * from sqlite_master
where type = 'table'
```

## Answer the following questions using SQL queries and pandas dataFrames generated from SQL queries.

1. How many different petitions in this database?

```{sql connection=conn}
select count(*)
from petitionInfo
```

2. What is the petition with the largest number of signatures? What the petition is about?
```{sql connection=conn}
select * from signature
order by signature_count desc
limit 5
```
```{sql connection=conn}
select * from petitionInfo
order by signature_count desc
limit 5
```

```{sql connection=conn}
select action, signature_count from petitionInfo
where signature_count = 607349
```


3. For the petition above (2.), which electoral constituency had the largest number of signatures? What's the number of signatures?

```{sql connection=conn}
select * from signature
group by signature.ons_code
order by signature.signature_count desc
```

4. Who is the MP of the constituency (3.)?
```{sql connection=conn}
select ons_code, mp from constituency
where ons_code == "E14000720"
```

5. Find out how many peitions are about election by searching the `action` column in one of tables.
```{sql connection=conn}
select count(*) as no_election
from petitionInfo
where action like '%election' OR action LIKE '%elect%'
```

6. Find whether there are correlations between the parties representing electoral constituencies and the number of signatures for the petition(s) you find (5.)
```{sql connection=conn}

```



